---
title: "fingerprintr"
author: "Karen Kafadar, Karen Pan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fingerprintr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contains code for the Contrast Gradient Algorithm (manuscript in preparation) for fingerprint minutiae quality scores. There is one main function for outputting quality metrics and several helper functions.

We would like to thank Dr. Adele Peskin for vital discussion and conversation leading to the creation and development of the Contrast Gradient Algorithm as well as an unpublished manuscript.


## Examples

```{r ex, include = TRUE}
# load image
#library(bmp)
G080_image <- read.bmp("data/G080.bmp")
# convert to text
image_file <- convert_image(G080_image, "bmp")

# load minutiae, already in matrix format
data(G080_min)

# quality scores
quality_scores(image_file, G080_min)
```

